---
title: "Presentation title"
subtitle: "Presentation subtitle"
author: "Author Name"
institute: "BERRI Limited"
date: "Presentation Date"
output:
  xaringan::moon_reader:
    css: 
      - default
      - css/nhsr.css
      - css/nhsr-fonts.css
    lib_dir: libs
    seal: false
    nature:
      highlightStyle: rainbow
      highlightLines: true
      highlightLanguage: ["r"]
      countIncrementalSlides: false
      ratio: "16:9"
    includes:
      after_body: [css/insert-logo.html]
---

```{r setup, include = FALSE}
library(knitr)
library(tidyverse)
library(NHSRtheme)
library(emo)
library(emojifont)
library(xaringanExtra)
xaringanExtra::use_tile_view()
xaringanExtra::use_panelset()
# set default options
opts_chunk$set(echo = FALSE,
               fig.width = 7.252,
               fig.height = 4,
               dpi = 300)

# uncomment the following lines if you want to use the NHS-R theme colours by default
# scale_fill_continuous <- partial(scale_fill_nhs, discrete = FALSE)
# scale_fill_discrete <- partial(scale_fill_nhs, discrete = TRUE)
# scale_colour_continuous <- partial(scale_colour_nhs, discrete = FALSE)
# scale_colour_discrete <- partial(scale_colour_nhs, discrete = TRUE)
```

class: title-slide, left, bottom

# `r rmarkdown::metadata$title`
----
## **`r rmarkdown::metadata$subtitle`**
### `r rmarkdown::metadata$author`
### `r rmarkdown::metadata$date`

---
class: inverse, middle, center

# An inverse slide

Often used for transitions

???
This is an example of presenter notes

---

# A slide where bullets appear

--

* first point

--

* second point

--

* third point

---
class: center, middle

# A slide with centered content and aligned with the middle 

This content is also centered and aligned with the middle of the slide

.left[We can start writing a sentence on the left...]
.right[...and end it on the right.]

---
class: center, middle
background-image:url(img/bethsimage.jfif)
background-size: contain

## About me

Bethany Pittuck

Assistant Psychologist Research 

Bsc(Hons) Psychology - University of Greenwich 

---
class: center, middle

`r emo::ji("tada")`

---

.pull-left[
# Some content on the left
]

--

.pull-right[
# Some content on the right
]

---
.pull-left[

.pull-left[
# first column
]
.pull-right[
# second column
]

]

.pull-right[

.pull-left[
# third column
]
.pull-right[
# fourth column
]

]

---

```{r echo=TRUE}
NHSRdatasets::LOS_model %>%
  head() #<<
```

---

# This slide has panels 

.panelset[

.panel[.panel-name[Tab 1]

Content for Tab 1
] <!-- end of panel-->
.panel[.panel-name[Tab 2]

Content for Tab 2
] <!-- end of panel-->
.panel[.panel-name[Tab 3]

Content for Tab 3
] <!-- end of panel-->
.panel[.panel-name[Tab 4]

Content for Tab 4

.pull-left[
Pulling content to the left
]

.pull-right[
Pulling content to the right
]
] <!-- end of panel-->

]

---